Implementation of Parallel Algorithms for ARIMA in Distributed Database Systems

### 2013-10-04 draft.tex
use the template
Added a table

\documentclass[english,12pt]{article}

@@

\begin{figure}[ht]
  \begin{centering}
    \includegraphics[angle=-90,scale=0.4]{pg_time_vs_size}
  \end{centering}
  \caption{\label{fig:gp_time_size} We fit a time series with length
    of $10^8$ using different chunk sizes. The execution times are
    around $400$ $\sim$ $500$ secs, and are quite stable. }
\end{figure}

>>>>

\documentclass[english,10pt]{llncs}

@@

\begin{figure}[ht]
  \begin{centering}
    \includegraphics[angle=-90,scale=0.4]{pg_time_vs_size}
  \end{centering}
  \caption{\label{fig:pg_time_size} We fit a time series with length of
    $10^8$ using different chunk sizes. The execution times are around
    $400$ $\sim$ $500$ secs, and are quite stable. }
\end{figure}

\begin{table}[ht]
  \begin{tabular}{|l|l|l|l|}
    \hline
    ~ & MADlib on GPDB & MADlib on Postgres & R's arima function \\ \hline
    Execution Time (sec) & 364.4 & 1391.9 & 1964.4 \\ \hline
  \end{tabular}
  \caption{\label{tbl:compare_R} Here we compare the execution times of ARIMA model fitting in R and in MADlib on Greenplum Database and PostgreSQL database. }
\end{table}
